Fivebranes

### 2022-03-15 fivebranes/index.tex
edited large N
typo
cleaning

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
In full generality, we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.

The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\mu, \Omega, \phi_\pm)$ which consist of even Dolbeault forms of type $(1,1)$ and $(0,2)$ on $X$:
\[
\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_+,\phi_-) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \mu + \dbar \Omega & = 0 \\
\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
\end{split}
\eeqn

@@

\begin{lem}
The $\Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\[
\Pi \Omega^{2,hol}_{cl} (\Hat{D}^3) \oplus \Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2 .
\]
\end{lem}

@@

In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
\brian{recall}

@@

The index we compute has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the Cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $q$ denotes a generator for the Cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}
These $U(1)$ weights are summarized in table \ref{tbl:weights1}.

\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
\end{tabular}
\end{center}

@@

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
\[
q^{3/2}\frac{r + r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

@@

\begin{itemize}
\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
\[
q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
\[
q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
\[
q^{3}\frac{q^{1/2} r + q^{1/2} r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

\begin{conj}
The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
\[
{\rm PExp} \left[f_{two} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{conj}

@@

  \[ \operatorname{PExp} \left (\frac{r^{3}\left (\begin{aligned} & t_{1}^{-1}r+t_{1}t_{2}^{-1}r+t_{2}r+q^{-1}r^{-3/2}+qr^{-3/2} \\  - & t_{1}r^{-1}-t_{1}^{-1}t_{2}r^{-1}-t_{2}^{-1}r^{-1}-qr^{3/2}-q^{-1}r^{3/2}
          \end{aligned}\right)}{(1-t_{1}^{-1}r)(1-t_{2}r)(1-t_{1}t_{2}^{-1}r)(1-r^{3/2}q)(1-r^{3/2}q^{-1})}\right ).\]
  \end{prop}

>>>>

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.

The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
\[
\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \mu + \dbar \Omega & = 0 \\
\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
\end{split}
\eeqn

@@

@@

We now consider the case $X = \C^3$ and consider the local operators of the single fivebrane theory supported at $0 \in \C^3$.

\begin{lem}
\label{lem:single}
The $\Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\beqn\label{eqn:localfree}
\Pi \Omega^{2,hol}_{cl} (\Hat{D}^3) \oplus \Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2 .
\eeqn
\end{lem}

@@

In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
We recount how it acts on the vector space \eqref{eqn:localfree}.

Recall that the even part of $E(3|6)$ consists of two summands:
\[
\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
\]
Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_1,r_2\}$ as the fundamental $\lie{sl}(2)$ representation.

@@

We consider the equivariant character of local operators on the holomorphic twist of a single fivebrane with respect to the following finite dimensional subalgebra of $E(3|6)$ 
\[
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset E(3|6) 
\]
which embeds in the following way: 
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect(\Hat{D}^3)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ is the subalgebra of $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$ consisting of constant formal series. 
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by Euler vector field $\sum_i z_i \frac{\del}{\del z_i} \in \Vect(\Hat{D}^3).$
\end{itemize}

Accordingly, the equivariant character we has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which acts by vector fields on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_1,r_2\}$. 
  \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
\end{itemize}
The weights are summarized in table \ref{tbl:weights1}.
Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
  \hline
  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
\end{tabular}
\caption{Fugacities for a single fivebrane.}
\end{center}
\label{tbl:weights1}
\end{table}

We now move on to the computation of the character of local operators on a single fivebrane.
According to the weights listed above and using the description of local operators in Lemma \label{lem:single} we have the following contributions to the character.

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
\[
q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

@@

\begin{itemize}
\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
\[
q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
\[
q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
\[
q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

\begin{conj}
The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
\[
{\rm PExp} \left[f_{two} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{conj}

@@

  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}q+t_{1}t_{2}^{-1}q+t_{2}q+r^{-1}q^{-3/2}+rq^{-3/2} \\  - & t_{1}q^{-1}-t_{1}^{-1}t_{2}q^{-1}-t_{2}^{-1}q^{-1}-rq^{3/2}-r^{-1}q^{3/2}
          \end{aligned}\right)}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}\right ).\]
  \end{prop}
